Covariate analysis of CMC RNASeq data reprocessed with Star-Feature counts pipeline (DLPFC with TMM normlaisation and Custom Design 1)

### 2016-11-07 code/Rmd/CMC_DLPFC_StarAligned_TMM_CD1.Rmd
Minor bug fix

### Normalisation (custom design)
Normalising COUNTS with a custom design matrix. Here Instituiton, Gender, LibraryBatch, Age\\_of\\_Death, PMI, RIN, RIN2, EV.1, EV.2, EV.3, EV.4, EV.5 are adjusted conditioned on Dx.Tissue
```{r customNorm, results='asis'}
# Primary variable of interest
postAdjustCovars = c('Dx.Tissue', 'Institution', 'Gender', 'LibraryBatch', 'Age_of_Death',
                     'PMI', 'RIN', 'RIN2', 'EV.1', 'EV.2', 'EV.3', 'EV.4', 'EV.5');

# Assign residual covariates
residualSigCovars = preAdjustedSigCovars
covariatesEffects = residualSigCovars$Effects.significantCovars[setdiff(residualSigCovars$significantCovars, postAdjustCovars)]
postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects))) %>% unique()

>>>>

### Normalisation (custom design)
Normalising COUNTS with a custom design matrix. Here Instituiton, Gender, LibraryBatch, Age\\_of\\_Death, PMI, RIN, RIN2, EV.1, EV.2, EV.3, EV.4, EV.5 are adjusted conditioned on Dx
```{r customNorm, results='asis'}
# Primary variable of interest
postAdjustCovars = c('Dx', 'Institution', 'Gender', 'LibraryBatch', 'Age_of_Death',
                     'PMI', 'RIN', 'RIN2', 'EV.1', 'EV.2', 'EV.3', 'EV.4', 'EV.5');
